### 2021-05-23 code/manuscript.Rmd
small model fixes

    # Automic model selection via likelihood ratio tests
    # using an alpha level of .20 (see Matuschek et al., 2017, J Mem Lang)
    cl <- makeCluster(n_cores)
    build <- buildmer(
      formula = formula_lme,
      data = trials,
      buildmerControl = buildmerControl(
        direction = c("backward", "backward"),
        cl = cl,
        crit = "LRT",
        elim = function(logp) exp(logp) >= .20,
        quiet = TRUE,
        calc.anova = TRUE,
        ddf = "Satterthwaite",
        REML = FALSE,
      ),
      control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
    )
    stopCluster(cl)

@@

    # Return a list of relevant model outputs
    return(
      list(
        model = build@model,
        anova = build@anova,
        summary = build@summary,
        means = em$emmeans,
        contrasts = em$contrasts
      )
    )
  }) %>%

@@

# Fit Bayesian mixed model
mod_brm <- brm(
  formula = form,
  data = trials,
  family = gaussian(),
  prior = prior,
  sample_prior = "yes",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  # iter = 20000,
  # warmup = 2000,
  cores = 4,
  backend = "cmdstanr"
)

>>>>

    # Automic model selection via likelihood ratio tests
    # using an alpha level of .20 (see Matuschek et al., 2017, J Mem Lang)
    cl <- makeCluster(n_cores)
    build <- buildmer(
      formula = formula_lme,
      data = trials,
      buildmerControl = buildmerControl(
        direction = c("backward", "backward"),
        cl = cl,
        crit = "LRT",
        elim = function(logp) exp(logp) >= .20,
        calc.anova = TRUE,
        ddf = "Satterthwaite",
        REML = FALSE,
      ),
      control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
    )
    stopCluster(cl)

@@

    # Return a list of relevant model outputs
    return(
      list(
        model = build@model,
        anova = build@anova,
        summary = build@summary,
        means = as.data.frame(em$emmeans),
        contrasts = as.data.frame(em$contrasts)
      )
    )
  }) %>%

@@

# Fit Bayesian mixed model
mod_brm <- brm(
  formula = form,
  data = trials,
  family = gaussian(),
  prior = prior,
  sample_prior = "yes",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  # iter = 20000,
  # warmup = 2000,
  # cores = 4,
  backend = "cmdstanr"
)
